---
title: "Overages Report for OLD NAVY"
output: pdf_document
---

```{r, echo = FALSE, message=FALSE, warning=FALSE}

library(dplyr)
library(readr)
library(rChoiceDialogs)
library(xtable)
library(scales)
options(digits =3, scipen = 7, big.mark= ",")


choose_file_directory <- function()
{
  v <- jchoose.dir()
  return(v)
}

```


```{r, echo=FALSE}
load(file = "Overages_Git.rtf")

Overages2 <- Overages_Git
Overages2$Program_Type <- trimws(Overages2$Program_Type, which = "both")

Overages2 <- Overages2 %>% subset( BRD_NM == "OLD NAVY") %>%
              subset(BRD_DIV_DESC != "FUN ZONE")%>% 
              subset(Program_Type != "VMI") %>%
              subset(XPLD_LN_ORD_QTY != 0) %>%
              subset(INV_RCPT_QTY != 0) %>%
              na.omit() %>%
              droplevels()

Overages2$INV_RCPT_QTY <- as.numeric(Overages2$INV_RCPT_QTY)
Overages2$XPLD_LN_ORD_QTY <- as.numeric(Overages2$XPLD_LN_ORD_QTY)
Overages2$ORIGIN_COUNTRY_CODE <- as.factor(Overages2$ORIGIN_COUNTRY_CODE)
Overages2$Total_FCST_ELC <- as.numeric(Overages2$Total_FCST_ELC)
```

  Data was pulled from the Inbound Unit Forecast table and compared against RMS _TDITW_ table in EDW for DPO's with a _Planned Stock Date_ between 8/2/1015 and 7/30/2016. Ordered Units (_XPLD LN ORD Qty_) were compared to Adjusted Receipt Units (_INV RCPT QTY_) for OLD NAVY to understand the percent difference of units ordered versus recieved. 

Taking a quick look at these data, after removing "FUNZONE" and VMI, to check that these have been excluded.
```{r, echo=FALSE}
# Check droped records
Overages2 %>% group_by(BRD_DIV_DESC) %>% 
  summarise("Units" = sum(INV_RCPT_QTY, na.rm=TRUE))%>% 
  as.data.frame()%>%
  knitr::kable()
Overages2 %>% group_by(Program_Type) %>% 
  summarise("Units" = sum(INV_RCPT_QTY, na.rm=TRUE))%>% 
  as.data.frame()%>%
  knitr::kable()
```

And checking that we have only **OLD NAVY** and also the proper unit count.
```{r, echo=FALSE}
Overages2 %>% 
  group_by(BRD_NM) %>% 
  summarise("Units" = sum(INV_RCPT_QTY, na.rm=TRUE))%>% 
  as.data.frame()%>%
  knitr::kable()

```

Now we can calculate the percent difference between Order Qty and Receipt Qty in order to plot a frequency distribution of the results. 
```{r, echo=TRUE}
Overages2 <- Overages2 %>% 
  mutate("Percent_diff" = ((INV_RCPT_QTY-XPLD_LN_ORD_QTY)/XPLD_LN_ORD_QTY)*100)
Overages2 <- Overages2 %>% 
  mutate("Delta_Units" = (INV_RCPT_QTY - XPLD_LN_ORD_QTY))

```

```{r, echo=FALSE}
count_of_dupes <- count(Overages2, MKT_PO_ID)

Overages_nodupe <- left_join(Overages2, count_of_dupes, by = "MKT_PO_ID" ) %>% droplevels()
Overages_nodupe <- subset(Overages_nodupe, n == 1)
Overages_nodupe$n <- as.factor(Overages_nodupe$n)

Overages_nodupe <- Overages_nodupe[order(-Overages_nodupe$Percent_diff), ]
```

Finally, we take a look at the frequency distribution of the percent difference. 
```{r, echo=TRUE}
hist(Overages_nodupe$Percent_diff, 
     main = "Histogram of % Diff", 
     xlab = "Percent Difference", col = "#00009950", 
     plot = TRUE, xlim = c(-10, 30), ylim= c(0,3500), breaks= 1500, freq = TRUE)
axis(1, at=c(-5, 5))
```

It appears most PO's fall within the +- 5% tolerance allowed. However there seems to be a heavy skew toward +5%.

Now let's take a look at a quick summary to understand the extremes of these data.
```{r, echo=FALSE}
summary(Overages_nodupe)
```

There are still some large overages in these data. Now let's take a look at the impact of those. 
```{r, echo=FALSE}
Over_20 <- Overages_nodupe %>% subset(Percent_diff>20)
Over_5 <- Overages_nodupe %>% subset(Percent_diff>5)
Under_neg_5 <- Overages_nodupe %>% subset(Percent_diff < c(-5))
Under_neg_20 <- Overages_nodupe %>% subset(Percent_diff < c(-20))

Over_table_5 <- Over_5 %>% 
  select(BRD_NM, XPLD_LN_ORD_QTY, INV_RCPT_QTY, Percent_diff, Delta_Units ) %>%
  group_by(BRD_NM) %>%
  summarise(sum_XPLD_LN_ORD_QTY = sum(XPLD_LN_ORD_QTY), sum_INV_RCPT_QTY = sum(INV_RCPT_QTY), sum_Delta_Units = sum(Delta_Units))

Over_table_20 <- Over_20 %>% 
  select(BRD_NM, XPLD_LN_ORD_QTY, INV_RCPT_QTY, Percent_diff, Delta_Units ) %>%
  group_by(BRD_NM) %>%
  summarise(sum_XPLD_LN_ORD_QTY = sum(XPLD_LN_ORD_QTY), sum_INV_RCPT_QTY = sum(INV_RCPT_QTY), sum_Delta_Units = sum(Delta_Units))

Under_table_20 <- Under_neg_20 %>% 
  select(BRD_NM, XPLD_LN_ORD_QTY, INV_RCPT_QTY, Percent_diff, Delta_Units ) %>%
  group_by(BRD_NM) %>%
  summarise(sum_XPLD_LN_ORD_QTY = sum(XPLD_LN_ORD_QTY), sum_INV_RCPT_QTY = sum(INV_RCPT_QTY), sum_Delta_Units = sum(Delta_Units))

Under_table_5 <- Under_neg_5 %>% 
  select(BRD_NM, XPLD_LN_ORD_QTY, INV_RCPT_QTY, Percent_diff, Delta_Units ) %>%
  group_by(BRD_NM) %>%
  summarise(sum_XPLD_LN_ORD_QTY = sum(XPLD_LN_ORD_QTY), sum_INV_RCPT_QTY = sum(INV_RCPT_QTY), sum_Delta_Units = sum(Delta_Units))

```

We cab calculate the Unit impact of PO's with over 20% delta.
```{r, echo= FALSE}
Over_table_20 %>% 
  as.data.frame()

```
And also PO's over the 5% threshold.
```{r, echo=FALSE}
Over_table_5%>% 
  as.data.frame()
```
For good measure let's look at the negative values we noted before. First Unit impact of PO's under -20%.
```{r, echo=FALSE}
Under_table_20%>% 
  as.data.frame()
```

Next under -5%.
```{r, echo=FALSE}
Under_table_5%>% 
  as.data.frame()
```
Now what are the Total Delta Units (including negative values) for the entire dataset:
```{r, echo=FALSE}
Overages_nodupe %>% 
  summarise(Summary_of_Delta = sum(Delta_Units)) 
```

Let's also consider the Total Overages (Percent Delta > 0) for the entire data set:
```{r, echo=FALSE}
Total_overage <- Overages_nodupe %>% subset(Delta_Units > 0) %>% 
  summarise(Summary_of_Delta = sum(Delta_Units))%>%
  as.data.frame()
 
```

```{r, echo=FALSE}
Overages_nodupe %>% subset(Delta_Units > 0) %>% 
  summarise(Summary_of_Delta = sum(Delta_Units))
```

...And Total Underage (Percent Delta < 0) for the entire data set:
```{r, echo=FALSE}
Overages_nodupe %>% subset(Delta_Units < 0) %>% summarise(Summary_of_Delta = sum(Delta_Units))


```

So...

> `r Overages_nodupe %>% subset(Delta_Units > 0) %>% summarise(Summary_of_Delta = sum(Delta_Units))` + `r Overages_nodupe %>% subset(Delta_Units < 0) %>% summarise(Summary_of_Delta = sum(Delta_Units))` = `r Total_overage`.

We can see that there are still a few PO's with large overages (> 20%). But as we learned the number of units over 20% (`r format(round(Over_table_20$sum_Delta_Units, digits = 0), big.mark= ",")`) over the total number of units over (`r format(round(Total_overage, digits = 0), big.mark= ",")`), we see that the over 20% units contribute only `r (Over_table_20$sum_Delta_Units/Total_overage)*100` percent to the total overage.


Lastly, We can take a look at the top ten Vendor's with large delta's (> 10,000) and percent difference greater zero to calculate their mean percent difference. 

```{r}
Overages_nodupe %>%   
  mutate(PAR_VENDOR_LEGAL_DESC = replace(PAR_VENDOR_LEGAL_DESC, 
      PAR_VENDOR_LEGAL_DESC=="TETS N RAI", "TETS N RAI INTERNATIONAL"))%>%
  group_by(PAR_VENDOR_LEGAL_DESC)%>%
  subset(Percent_diff >= 0) %>%
  summarise(Summary_of_Delta = sum(Delta_Units), 
            mean_percent_diff = mean(Percent_diff)) %>%
  subset(Summary_of_Delta > 10000) %>%
  arrange(desc(mean_percent_diff))%>%
  head(n=10) %>%
  knitr::kable()
```

