---
title: "Overages Report for OLD NAVY"
output:
    pdf_document
---
\setlength\parindent{24pt}



```{r, echo = FALSE, message=FALSE, warning=FALSE}

library(dplyr)
library(readr)
library(rChoiceDialogs)
library(xtable)
library(scales)
options(digits =3, scipen = 7, big.mark= ",")


choose_file_directory <- function()
{
  v <- jchoose.dir()
  return(v)
}

```


```{r, echo=FALSE}
load(file = "Overages_Git.rtf")

Overages2 <- Overages_Git
Overages2$Program_Type <- trimws(Overages2$Program_Type, which = "both")

Overages2 <- Overages2 %>% subset( BRD_NM == "OLD NAVY") %>%
              subset(BRD_DIV_DESC != "FUN ZONE")%>% 
              subset(Program_Type != "VMI") %>%
              subset(XPLD_LN_ORD_QTY != 0) %>%
              subset(INV_RCPT_QTY != 0) %>%
              na.omit() %>%
              droplevels()

Overages2$INV_RCPT_QTY <- as.numeric(Overages2$INV_RCPT_QTY)
Overages2$XPLD_LN_ORD_QTY <- as.numeric(Overages2$XPLD_LN_ORD_QTY)
Overages2$ORIGIN_COUNTRY_CODE <- as.factor(Overages2$ORIGIN_COUNTRY_CODE)
Overages2$Total_FCST_ELC <- as.numeric(Overages2$Total_FCST_ELC)
```

```{r, echo= FALSE}
Overages2 <- Overages2 %>% 
  mutate("Percent_diff" = ((INV_RCPT_QTY-XPLD_LN_ORD_QTY)/XPLD_LN_ORD_QTY)*100)
Overages2 <- Overages2 %>% 
  mutate("Delta_Units" = (INV_RCPT_QTY - XPLD_LN_ORD_QTY))

```

```{r, echo=FALSE}
count_of_dupes <- count(Overages2, MKT_PO_ID)

Overages_nodupe <- left_join(Overages2, count_of_dupes, by = "MKT_PO_ID" ) %>% droplevels()
Overages_nodupe <- subset(Overages_nodupe, n == 1)
Overages_nodupe$n <- as.factor(Overages_nodupe$n)

Overages_nodupe <- Overages_nodupe[order(-Overages_nodupe$Percent_diff), ]
```

```{r, echo=FALSE}
Over_20 <- Overages_nodupe %>% subset(Percent_diff>=20)
Over_5 <- Overages_nodupe %>% subset(Percent_diff>=5)
Under_neg_5 <- Overages_nodupe %>% subset(Percent_diff <= c(-5))
Under_neg_20 <- Overages_nodupe %>% subset(Percent_diff <= c(-20))

Over_table_5 <- Over_5 %>% 
  select(BRD_NM, XPLD_LN_ORD_QTY, INV_RCPT_QTY, Percent_diff, Delta_Units ) %>%
  group_by(BRD_NM) %>%
  summarise(sum_XPLD_LN_ORD_QTY = sum(XPLD_LN_ORD_QTY), sum_INV_RCPT_QTY = sum(INV_RCPT_QTY), sum_Delta_Units = sum(Delta_Units))

Over_table_20 <- Over_20 %>% 
  select(BRD_NM, XPLD_LN_ORD_QTY, INV_RCPT_QTY, Percent_diff, Delta_Units ) %>%
  group_by(BRD_NM) %>%
  summarise(sum_XPLD_LN_ORD_QTY = sum(XPLD_LN_ORD_QTY), sum_INV_RCPT_QTY = sum(INV_RCPT_QTY), sum_Delta_Units = sum(Delta_Units))

Under_table_20 <- Under_neg_20 %>% 
  select(BRD_NM, XPLD_LN_ORD_QTY, INV_RCPT_QTY, Percent_diff, Delta_Units ) %>%
  group_by(BRD_NM) %>%
  summarise(sum_XPLD_LN_ORD_QTY = sum(XPLD_LN_ORD_QTY), sum_INV_RCPT_QTY = sum(INV_RCPT_QTY), sum_Delta_Units = sum(Delta_Units))

Under_table_5 <- Under_neg_5 %>% 
  select(BRD_NM, XPLD_LN_ORD_QTY, INV_RCPT_QTY, Percent_diff, Delta_Units ) %>%
  group_by(BRD_NM) %>%
  summarise(sum_XPLD_LN_ORD_QTY = sum(XPLD_LN_ORD_QTY), sum_INV_RCPT_QTY = sum(INV_RCPT_QTY), sum_Delta_Units = sum(Delta_Units))

```

  Data was pulled from the Inbound Unit Forecast table and compared against RMS _TDITW_ table in EDW for DPO's with a _Planned Stock Date_ between 8/2/1015 and 7/30/2016. Ordered Units (_XPLD LN ORD Qty_) were compared to Adjusted Receipt Units (_INV RCPT QTY_) for OLD NAVY to understand the percent difference of units ordered versus recieved. 
  
```{r, echo=FALSE}
Total_overage <- Overages_nodupe %>% subset(Delta_Units > 0) %>% 
  summarise(Summary_of_Delta = sum(Delta_Units))%>%
  as.data.frame()
```



We observed, that there are still a few PO's with large overages (> 20%). However, the number of units over 20% (`r format(round(Over_table_20$sum_Delta_Units, digits = 0), big.mark= ",")`) divided by the total "overage"" units (`r format(round(Total_overage, digits = 0), big.mark= ",")`), we see that the over 20% units contribute only `r (Over_table_20$sum_Delta_Units/Total_overage)*100`% to the total overage and only `r (Over_table_20$sum_Delta_Units/sum(Overages2$XPLD_LN_ORD_QTY))*100`% of the total order qty.


Now we can calculate the percent difference between Order Qty and Receipt Qty in order to plot a frequency distribution of the results. Taking a look at the frequency distribution of the percent difference. 




```{r, echo=FALSE}
hist(Overages_nodupe$Percent_diff, 
     main = "Histogram of % Diff", 
     xlab = "Percent Difference", col = "#00009950",
     ylab = "Frequency by PO",
     plot = TRUE, xlim = c(-10, 30), ylim= c(0,3500), breaks= 1500, freq = TRUE)
axis(1, at=c(-5, 5))
```

It appears most PO's fall within the +- 5% tolerance allowed. However there seems to be a heavy skew toward +5%.

 Looking into the details, we see that the max percent overage for all DPO's is `r max(Overages_nodupe$Percent_diff)`% and the min is `r min(Overages_nodupe$Percent_diff)`%. So there are still some extremes. And since we are interested in large overages, let's take a look at the unit count of those.

```{r include=FALSE}
mx <- Overages_nodupe$Percent_diff
my <- Overages_nodupe$Delta_Units

h <- Overages_nodupe$Percent_diff %>% 
  subset(Overages_nodupe$Percent_diff > 0) %>% 
  hist( main = "Histogram of % Diff", 
        xlab = "Percent Difference", 
        col = "#00009950", 
        plot = TRUE, 
        xlim = c(-10, 50), 
        ylim= c(0,5500), 
        breaks= c(0,1,2,3,4,5,10,15,20,Inf), freq = FALSE)
```

\pagebreak

Taking a look at the breakdown by units for each bucket created by the Percent difference from 0% to > 20%:

```{r include=FALSE}
breaks <- data.frame("beg"= h$breaks[-length(h$breaks)], "end"=h$breaks[-1])
# counts <- data.frame("beg"= h$counts[-length(h$counts)], "end"=h$counts[-1])

sums <- apply(breaks, MARGIN=1, FUN=function(x) { sum(my[ mx >= x[1] & mx < x[2] ]) })

#Total_overage <- Overages_nodupe %>% subset(Delta_Units > 0) %>% 
  #summarise(Summary_of_Delta = sum(Delta_Units))
# sums[10] <- Total_overage - sum(sums)
h$counts <- sums
plot(x=h$breaks[1:9], y=h$counts, xlab = "% Percent Difference", ylab="Sum of Units", main="Delta Units vs Percent Difference", xlim = c(0, 20))

```

```{r include=FALSE}
buckets <- apply(breaks, MARGIN=1, FUN=function(x) {paste(x[1], "to", x[2])})
h_table <- buckets[1:9]
h_table <- as.data.frame(h_table)
h_table[,2] <- h$counts
names(h_table) <- c("Percent Bucket", "Unit Count")
h_table %>% knitr::kable()
```

```{r include=FALSE}
mx <- Overages_nodupe$Percent_diff
my <- Overages_nodupe$Delta_Units

h <- Overages_nodupe$Percent_diff %>% 
  subset(Overages_nodupe$Percent_diff > 0) %>% 
  hist( main = "Histogram of % Diff", 
        xlab = "Percent Difference", 
        col = "#00009950", 
        plot = TRUE, 
        xlim = c(-10, 50), 
        ylim= c(0,5500), 
        breaks= c(0,1,2,3,4,5,10,15,20,Inf), freq = FALSE)
```
```{r include=FALSE}
  breaks <- data.frame("beg"= h$breaks[-length(h$breaks)], "end"=h$breaks[-1])
  # counts <- data.frame("beg"= h$counts[-length(h$counts)], "end"=h$counts[-1])
  
  sums <- apply(breaks, MARGIN=1, FUN=function(x) { sum(my[ mx >= x[1] & mx < x[2] ]) })
  
  #Total_overage <- Overages_nodupe %>% subset(Delta_Units > 0) %>% 
  #summarise(Summary_of_Delta = sum(Delta_Units))
  # sums[10] <- Total_overage - sum(sums)
  # h$sums <- sums
  plot(x=h$breaks[1:9], y=h$counts, xlab = "% Percent Difference", ylab="Sum of Units", main="Delta Units vs Percent Difference", xlim = c(0, 20))
```
```{r echo=FALSE} 
  buckets <- apply(breaks, MARGIN=1, FUN=function(x) {paste(x[1], "to", x[2])})
  # h_table <- buckets[1:9]
  # h_table <- as.data.frame(h_table)
  # h_table[,2] <- h$counts
perc_total <- (h$counts/sum(h$counts))*100
  h_table <- as.data.frame(cbind(buckets[1:9], format(floor(h$counts), big.mark = ","), format(perc_total, digits = 1), format(floor(sums[1:9]), big.mark = ",")))

names(h_table) <- c("Percent Bucket", "Count of PO's", "Percent Total", "Unit Count")
h_table %>% knitr::kable(align='r')
```

We can calculate the Unit impact of PO's with over 20% delta.

```{r, echo= FALSE}
Over_table_20 %>% 
  as.data.frame()

```

And also PO's over the 5% threshold.

```{r, echo=FALSE}
Over_table_5%>% 
  as.data.frame()
```

Now, what is the net Delta Units (including negative values) for the entire dataset?:

```{r, echo=FALSE}
Overages_nodupe %>% 
  summarise(Summary_of_Delta = sum(Delta_Units)) 
```

Let's also consider the Total Overages (Percent Delta > 0) for the entire data set:

```{r, echo=FALSE}
Total_overage
```


\pagebreak

As we noted, there seems to be a skew toward the +5% in the frequency distribution above. We should now take a look at the top ten Vendor's with large delta's (> 10,000)--and percent difference greater than zero--calculating their mean percent difference to find out who may be exploiting our allowance. 

```{r echo= FALSE}
Overages_nodupe %>%   
  mutate(PAR_VENDOR_LEGAL_DESC = replace(PAR_VENDOR_LEGAL_DESC, 
      PAR_VENDOR_LEGAL_DESC=="TETS N RAI", "TETS N RAI INTERNATIONAL"))%>%
  group_by(PAR_VENDOR_LEGAL_DESC)%>%
  subset(Percent_diff >= 0) %>%
  summarise(Summary_of_Delta = sum(Delta_Units), 
            mean_percent_diff = mean(Percent_diff)) %>%
  subset(Summary_of_Delta > 10000) %>%
  arrange(desc(mean_percent_diff))%>%
     rename("Parent Vendor" =PAR_VENDOR_LEGAL_DESC, 
          "Unit Difference"= Summary_of_Delta, 
          "Average % Difference"= mean_percent_diff) %>%
  head(n=10) %>%
  knitr::kable( format.args = list(big.mark = ','))
```

And by Origin Country...

```{r echo= FALSE}
Overages_nodupe %>%   
  group_by(ORIGIN_COUNTRY_CODE)%>%
  subset(Percent_diff >= 0) %>%
  summarise(Summary_of_Delta = sum(Delta_Units), 
            mean_percent_diff = mean(Percent_diff)) %>%
  subset(Summary_of_Delta > 10000) %>%
  arrange(desc(mean_percent_diff))%>%
   rename("Origin Country" =ORIGIN_COUNTRY_CODE, 
          "Unit Difference"= Summary_of_Delta, 
          "Average % Difference"= mean_percent_diff) %>%
  head(n=10) %>%
  knitr::kable( format.args = list(big.mark = ','))
```

\pagebreak

```{r include=FALSE}
mx <- Overages_nodupe$Percent_diff
my <- Overages_nodupe$Delta_Units

h <- Overages_nodupe$Percent_diff %>% 
  subset(Overages_nodupe$Percent_diff > 0) %>% 
  hist( main = "Histogram of % Diff", 
        xlab = "Percent Difference", 
        col = "#00009950", 
        plot = TRUE, 
        xlim = c(-10, 50), 
        ylim= c(0,5500), 
        breaks= c(0,1,2,3,4,5,10,15,20,Inf), freq = FALSE)
```
```{r include=FALSE}
  breaks <- data.frame("beg"= h$breaks[-length(h$breaks)], "end"=h$breaks[-1])
  # counts <- data.frame("beg"= h$counts[-length(h$counts)], "end"=h$counts[-1])
  
  sums <- apply(breaks, MARGIN=1, FUN=function(x) { sum(my[ mx >= x[1] & mx < x[2] ]) })
  
  #Total_overage <- Overages_nodupe %>% subset(Delta_Units > 0) %>% 
  #summarise(Summary_of_Delta = sum(Delta_Units))
  # sums[10] <- Total_overage - sum(sums)
  # h$sums <- sums
  plot(x=h$breaks[1:9], y=h$counts, xlab = "% Percent Difference", ylab="Sum of Units", main="Delta Units vs Percent Difference", xlim = c(0, 20))
```
```{r include =FALSE} 
  buckets <- apply(breaks, MARGIN=1, FUN=function(x) {paste(x[1], "to", x[2])})
  # h_table <- buckets[1:9]
  # h_table <- as.data.frame(h_table)
  # h_table[,2] <- h$counts
perc_total <- (h$counts/sum(h$counts))*100
  h_table <- as.data.frame(cbind(buckets[1:9], h$counts, perc_total, floor(sums[1:9])))

names(h_table) <- c("Percent Bucket", "Count of PO's", "Percent Total", "Unit Count")
  h_table %>% knitr::kable()
  
```



\pagebreak

```{r include=FALSE}
POs_Over_20 <- Overages_nodupe %>% subset(Percent_diff >=20)
```

Zooming in to see the large overages: 

```{r echo=FALSE}
hist(POs_Over_20$Percent_diff, 
     main = "Histogram of % Diff", 
     xlab = "Percent Difference", col = "#00009950",
     ylab = "Frequency by PO",
     plot = TRUE, xlim = c(20, 900), ylim= c(0,20), breaks= 120, freq = TRUE)
axis(1, at=c(20, 60, 100))
```

What we are seeing above, seems to be instances where DC's are accepting Units on comparable PO's (same pack factor and CC) but not the original. We know that this occurs from speaking to IM teams. 

Looking deeper, there are instances where there is an underage on a PO(s) and a overage on a different PO(s) with same style. I do not see *exactly* a one-to-one relationship in these data--though this seems to be an artifact of the time bound used. During a cursory look, it did hold true that the PO's in question are at the edges of the time bound. Would need to repull the data--matching at style level--to get an accurate summation.

Thank you!

\pagebreak

### Appendix

Taking a quick look at these data, after removing "FUNZONE" and VMI, to check that these have been excluded.

```{r, echo=FALSE}
# Check droped records
Overages2 %>% group_by(BRD_DIV_DESC) %>% 
  summarise("Units" = sum(INV_RCPT_QTY, na.rm=TRUE))%>% 
  as.data.frame()%>%
  knitr::kable( format.args = list(big.mark = ','))
Overages2 %>% group_by(Program_Type) %>% 
  summarise("Units" = sum(INV_RCPT_QTY, na.rm=TRUE))%>% 
  as.data.frame()%>%
  knitr::kable( format.args = list(big.mark = ','))
```

And checking that we have only **OLD NAVY** and also the proper unit count.

```{r, echo=FALSE}
Overages2 %>% 
  group_by(BRD_NM) %>% 
  summarise("Units" = sum(INV_RCPT_QTY, na.rm=TRUE))%>% 
  as.data.frame()%>%
  knitr::kable( format.args = list(big.mark = ','))

```


```{r include= FALSE}
POs_Over_20 <- Overages_nodupe %>% subset(Percent_diff >=20)
POs_Under_0 <- Overages_nodupe %>% subset(Percent_diff < 0)
Under_over_join <- left_join(POs_Over_20, POs_Under_0, by = "OPR_BRD_STY_ID")
Under_over_join <- subset(Under_over_join, n.y==1) 

knitr::kable(Under_over_join[, c(2, 6, 18, 24, 36 )])

```

